### 2017-10-11 Gruba/03-fe.tex

Different from the straightforward notions of \textit{Info Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users by their interested topics.
In short, with a given lexicon consisting of several \textit{topics}, the interest feature of a user is a normalized vector, in which each dimension refers to the probability that the said user matches a \textit{topic}.

>>>>

Different from the straightforward notions of \textit{Info Feature} and \textit{Behavior Feature}, \textit{Interest Feature} involves a process of labeling users by their interested topics.
In short, with a given lexicon(made by some professionals) consisting of several \textit{topics}, the interest feature of a user is a normalized vector, in which each dimension refers to the probability that the said user matches a \textit{topic}.
